\LARGE \bf Mixed Non-Bayesian and DeGroot Learning

### 2012-12-12 docs/paper.tex
Corrected standard deviation

We seek to investigate the behavior of a network consisting of nodes learning in the ``Non-Bayesian'' style of Jadbabaie et. al. with the added presence of DeGroot-style nodes.  These DeGroot nodes will make no observations about the state of the world and incorporate neighboring beliefs in a simple linear manner.  This can model social learning scenarios where some members of a network thoughtfully develop beliefs based on observations and advice, and others do nothing but naively pass along opinions.  What are the consequences of such naive agents in a social learning scenario?  Do certain network structures exacerbate their impact?  How many naive agents can be present before learning becomes prohibitively difficult?  In this work we investigate answers to these questions and propose our model of mixed Non-Bayesian and DeGroot learning as a tool for future research.

@@

@@

@@

\begin{figure*}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases. For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=5$. To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors. Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type. Unexpectedly, the time to convergence is inversely proportional to the ratio of Non-Bayesian nodes.}
\label{fig:nb_ratio}
\end{figure*}

@@

\begin{figure}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/dg_faster}}
\centering
\includegraphics[width=0.48\textwidth]{figures/dg_faster}
\caption{The average beliefs in $\Theta^*$, the true distribution, for the two types of nodes during simulations with 0\% and 20\% of DeGroot nodes in a complete graph. The possible distributions were Gaussians centered at 100 and 105 with $\sigma=1$. All random seeds were fixed such that in both runs the Non-Bayesian nodes received the exact same sequence of draws. DeGroot nodes' beliefs were estimated using the distance metric. The figure shows how DeGroot nodes help amplify the initial belief updates of Non-Bayesian nodes, which leads to overall faster convergence.}
\label{fig:dg_faster}
\end{figure}

>>>>

We seek to investigate the behavior of a network consisting of nodes learning in the ``Non-Bayesian'' style of Jadbabaie et. al. with the added presence of DeGroot-style nodes.  These DeGroot nodes will make no observations about the state of the world and incorporate neighboring beliefs in a simple linear manner.  This can model social learning scenarios where some members of a network thoughtfully develop beliefs based on observations and advice, and others do nothing but naively pass along opinions.  What are the consequences of such naive agents in a social learning scenario?  Do certain network structures exacerbate their impact?  How many naive agents can be present to significantly affect learning?  In this work we investigate answers to these questions and propose our model of mixed Non-Bayesian and DeGroot learning as a tool for future research.

@@

\begin{figure*}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence as the ratio of Non-Bayesian to DeGroot nodes decreases. For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=1$. To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors. Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type. Unexpectedly, the time to convergence is inversely proportional to the ratio of Non-Bayesian nodes.}
\label{fig:nb_ratio}
\end{figure*}

@@

\begin{figure*}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/convergence_time}}
\centering
\includegraphics[width=.9\textwidth]{figures/convergence_time}
\caption{Time to convergence as the size of the graph grows. Each datapoint is the average of 200 trials. For all trials the nodes had to distinguish between Gaussians centered at 100 and 105 with $\sigma=1$. DeGroot nodes were on average 20\% of the total vertices. Only 60\% of the Non-Bayesian nodes were receiving signals. We also show $R^2$ values for a linear regression for the different types of graph. We can see that the convergence time increases linearly with the size of the graph, and that the complete graph takes substantially longer to converge. }
\label{fig:convergence_time}
\end{figure*}

@@

@@
